Interactive Visual Analysis of Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-09-30 draft.tex
weakened some parts of the Results section

\section{\uppercase{Conclusion}}
\label{sec:Conclusion}
\noindent The presented results indicate that the image based variables \emph{torsion}, \emph{curvature} and \emph{curvature angle} are not enough to characterize pathological changes in the lumbar spine.
%%
They are well suited to characterize subject \emph{gender} due to their \emph{body size} difference using \emph{mean curvature} and \emph{mean curvature angle}.
%%
This is due to the higher curvature of smaller subjects and the significant difference of average \emph{body size} between males and females.
%%
\emph{Gender} was characterized well in the analysis of all subjects as well as subjects divided by \emph{BMI}.

Subjects grouped using \emph{body size} have a similar spine shape and a lower variance.
%%
The remaining information within these groups is not enough to characterize back pain-related variables.
%%
For some \emph{body size} groups, certain \emph{nutrition} or \emph{psychological} variables can be predicted with a comparatively high error.
%%

@@

%In our future work, we will focus on more precise models for extracting measures described in Section~\ref{sec:ProposedFeatures}.
In our future work, we will focus on more precise models for extracting measures.
%%
Dented vertebras are a early sign of a pathological deformation, so we want to capture this by segmenting the top and bottom point of each vertebra center.
%%
Another interesting metric is the spine canal thickness over the whole spine, capturing early signs of herniated disc disease.
%%
As another focus, we want to include the method into existing visual analytics methods designed for analyzing shape information for epidemiological data \cite{Klemm2014VIS}.
%%
\\\\
Combining the power of statistical analysis, visual analytics and data mining techniques is essential for analyzing increasingly complex heterogenous population data.
%%
These methods do not aim to replace the traditional epidemiological workflow, but rather intervenes at the weak points of standard statistical methods.
%%
Our method provides a novel way to gain insight into these complex data sets and amplifies hypotheses generation.

>>>>

\section{\uppercase{Conclusion}}
\label{sec:Conclusion}
\noindent The presented results indicate that the image based variables \emph{torsion}, \emph{curvature} and \emph{curvature angle} are not enough to characterize pathological changes in the lumbar spine in the given quality.
%%
They are associated with subject \emph{gender} due to their \emph{body size} difference using \emph{mean curvature} and \emph{mean curvature angle}.
%%
This is due to the higher curvature of smaller subjects and the significant difference of average \emph{body size} between males and females.
%%
\emph{Gender} was detected well in the analysis of all subjects as well as subjects divided by \emph{BMI}.

Subjects grouped using \emph{body size} have a similar spine shape and a lower variance.
%%
The remaining information within these groups is not enough to characterize back pain-related variables.
%%
Associations with certain \emph{nutrition} or \emph{psychological} variables can be observed with a comparatively high error for some \emph{body size} groups.
%For some \emph{body size} groups, certain \emph{nutrition} or \emph{psychological} variables can be predicted with a comparatively high error.
%%

@@

%In our future work, we will focus on more precise models for extracting measures described in Section~\ref{sec:ProposedFeatures}.
In our future work, we will focus on more precise models for extracting measures.
%%
Dented vertebras are a early sign of a pathological deformation, so we want to capture this by segmenting the top and bottom point of each vertebra center.
%%
Another interesting metric is the spine canal thickness over the whole spine, capturing early signs of herniated disc disease.
%%
As another focus, we want to include the method into existing visual analytics methods designed for analyzing shape information for epidemiological data \cite{Klemm2014VIS}.
%%
\\\\
Combining the power of statistical analysis, visual analytics and data mining techniques are essential for analyzing increasingly complex heterogenous population data.
%%
These methods do not aim to replace the traditional epidemiological workflow, but rather intervenes at the weak points of standard statistical methods.
%%
Our method provides a novel way to gain insight into these complex data sets and amplifies hypotheses generation.
